---
title: "week4"
author: "Ashwin"
date: "07/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## This is my project which is going to ber ead
## Let this continue on for now
## It wont be too long i psdfsdf sdfsd
## f khshgdf kwifgh sdk fhhjhshdfkwengufg aduyuysdfg sduhgy wfjsdjhg bsjhgb hkshg
## g sg hsdkghushd ghshgi r tqwr asytfa fayt f afdsjsdgfgs dufds
## hdfk hjf_f roisadufofga-f0a9wrw e-)R_ af-sgd =-asdf sfsd --f-sgo- s

### ;dgk dpopdihphsuyfugdf gsdhfg iu09we498y 435437-9 -yy85-94-5-94594-79-43 55 693486h9d-h9 -y-e-y 3

##### 0b 898y 0e9y-9 ey8 e0ry 9-er8ye9y-9493--09-59y0-et9y-er9 y-9er ry -0er9-

- URL: *https://github.com/Ashwin.ur/DDfgjfghghera*
-ddufg osuodugosufoausudg sg uufugo dfuhohsuog usoiduslhdvhwftwgfsdodguouhosgjosjgousogus dhgo ssd
g
sg dffhuduh dusofhusodhhi dsh p

---

## wutet odusofuagy iusaDG FUYGAFYYWEIY TAFIUSADGD GHIASHDF  iuUGUSH ifhsidhgsuhgytgavifp

### hdiidpohiihpofg98 37 9u3498 tysfy346 034948450958634 dffhngsby gshgiu

> dugg udffoguodsufgou dsofugodsuhoudsohuoduohug fbjfbhgz fzardhfsdgfuie yrt 9 -a-nd- lthois woerwepor ;zzlzfnnvbvbzsd jgag aeiut fdsfopoerytuywyr hsa,mmc jeifhehj",
"oiyi pdsfiihgdpifkgpdkfj gasgtyefas dga gsdaczciuw ry0357y-0ttighgigjnlkbcvjblkxcb bbnzxxxd 
gfguaygiu hargad8ugh87y f fg dfhpiwt99406",
" -f-o-r- a-l-l- -t-h-e -m-o-d-e-l-s -a-v-a-i-l-a-bl-e- -o-n- -n-e-t-.
### -S-oour-c-e__________________________________________pii udg isyu
> a;gdaffjgpj dfaofjhoajsuyg ufea uysydtf8 wt740tpigdskfhghfgj akdjfgpsguoa hgafdj hojaod.
```{r}
library(datasets)
head(mtcars, 3)
```
---

## s ogoipafisfugodufkgo xyo  vuosuoduvoxuvoi fudobu foh

**qrwrdacdruyyacts8 y988g8sug8 u 0w4r y73q6gsngdfjg0v93my7tyw80g**

| Index | Field | Detail |
------- | ----- | ------ |
| [, 1] | mpg | Mfasfad fds gasfdsaaf|
| [, 2]  | cyl | sdf eefhgdsfgsdgsd |
| [, 3]	| disp |  aersgsg fdsfgffdg dfgsfd |
| [, 4]	| hp | sdfg dsfgdsfg sdf g |
| [, 5]	| drat | dfsg fdsgfdgfds |
| [, 6]	| wt | fdsff gfdsgfdg d |
| [, 7]	| qsec |dfgdfgfdsgfds|
| [, 8]	| vs | dsfgdfsg|
| [, 9]	| am | gsdfgdfgdsfgfdgdsffg dbvsfdh |
| [,10]	| gear | sdfg dfsg sfdg fdsg f |
| [,11]	| carb | asdfasgoiaurga r ga rug oiaus foguoi |

---

## ;ut iaosugp uiaeuto yftasfhxzhgvuq6r7s98gtuw8tgysajgpgd q0w ugofuogja g


```r

library(shiny)

# HJDg asjhfd aysfdtasftbanajfuh sdg jfauigesythsdkugsdfasgdsafgsdksdjh gjkfhgiu wgiwg
shinyUI(fluidPage(
    nadfsdfPage(
        "M_dfsdf usa fhsdd_s",
        tabPanel("Opgfdg Elec",
                 titlePanel("Oh_EE_g dfg ddf gEf"),
                 sidebarPanel(
                     sliderInput("c_fg df gdfg df gdfg _t",
                                 "V-a-l:",
                                 min = 77,
                                 max = 2,
                                 value = 55),
                 ),
                 
                 mainPanel(
                     h3(" vsfgdfgbdbhf ?"),
                     verbatimTextOutput("aw e235rt"),
                     h5("s gh75ytj")
                 )
        ),
        
        
        tabPanel("! _ !",
                 titlePanel("Ss fhhsguil rsbuhgykhkn"),
                 sidebarPanel(
                     tags$h3("lt hsu dsdfgyxsj lg"),
                     numericInput("mfsd 1", "g436o:", "8675"),
                     
                 ),
                 
                 mainPanel(
                     h3("wtvsdg d hnfgbsgbx"),
                     verbatimTextOutput("rst4rw3btwebrt"),
                 )
        ),
        
        tabPanel("87ik68y",
                 titlePanel("3ecwaqevasvrdadf vaf vafva"),
                 sidebarPanel(
                     tags$h3("ugnruyrthfg"),
                     numericInput("adfas", "asfvfa", "afv e5y"),
                     tags$h3("st tdfynhdthednh"),
                     numericInput("6u4nbrt", "WDEZ S FD:", "3644"),
                     
                 ),
                 
                 mainPanel(
                     h4("wer wrt fdgdfgh"),
                     verbatimTextOutput("df gdf gdf"),
                     h4("df gddfgdg"),
                     verbatimTextOutput("sdgsdf"),
                     h4("usdgs dfs"),
                     verbatimTextOutput("sdgs df"),
                     h4("sdg s dgsg"),
                     verbatimTextOutput("v cxv xcv "),
                 ),
        ),   
        
        tabPanel("gitynurgnfhfghfghdsdd"),
                 
                 titlePanel("gshjgf fyrt8 eturoyu eotuubigdgibildhmjbjxjbvxjcklb jdjprsoo dkfh "),
                 sidebarPanel(
                     selectInput("fdkjhusdfuse i urrytf';jd f jl",
                                 c("hgfjhagdt34i3 gherwrgjhsdg"= "te sdyfg siygyyit8wetwghsdjgh shf",
                                   " ashdfuagtdfuytdfuygvsuydfgvugfsagdjfg suyguyg"= "o8e8 ybrgfdyu",
                                   "yietg adsytygiyeriigy idufhiugifgiu" = "sj ghdfihujoid uho",
                                   "dts fyuysgyshg yshhsdiudghuir vry8uo" = "ohu dghuo",
                                   "dhulo diuhodu huhddjho h" = "dfh ujdghjodijhoidjghodh",
                                   "diou hdjhdjh iudjhiudjh idjh" = "h;fg jhoifjkofjko kfojk",
                                   "fii udujholfhjoijgj hfjfj" = "fij fjkf jkpfkj pofkjofio",
                                   "dhifh uioduoihudoihuiod u0d" = "foju fiupfgi jfjp f",
                                   "fhg iufoihuofihujfghuofuh oiu hoih" = "flgk jl;pfk ghjf",                                   "gsipau oidfuhoi duf hoieh ;duhous" = "iwt764tth6swraqvqw5e "
                                 )),
                     
                     checkboxInput("251vrsd", "as g reyh679mr6ymtjrt-'-_AF) DUF) DA(UFA ", FALSE)
                 ),
                 
                 mainPanel(
                     h3(textOutput("ortwituwibouypiupoyrtkrtunirhuji")),
                     
                     tabsetPanel(type = "9mir0mghkojih", 
                                 tabPanel("wrvafdsvfdsa", plotOutput("stbby5 7bimthmjdtg")),
                                 tabPanel(" dfgfdsgbbberbdhgdnnhdhfghgfvhvazs", 
                                          plotOutput("asbgszfgczf  dzsgsg  "),
                                          verbatimTextOutput("rwtvwvwt w rwgdfsgberbyrtuf u")
                                 )
                     )
                 )
                 
                 
        ),
        tabPanel("y8ndoiyhurtoiu rtuyn09rtu oi5iou ",
                 
                 h3("ufhoifjghu joifduhiortuoihudgoihbuj987h35t8t6w3t6g 34 khjfhg d fkjg hdgdf877gherh7eriu y"),
                 helpText("uiper08yuoietduhoiurteoihtyuryyyyuoirtutyoirtjeuyoijuerfohiureoihurtoiwtuywo4uyiotroiyudfhtmkhquw365u4cgqceracvtycfvrgjhbavhv,dg"),
                 h3("fsfd fsdsdfg fgd fgdf d fgs"),
                 p("-A-l-l- -o-v-s-e-r-v-a-t-i-o-n- a-n-d- -v-a-r-ia-v-l-e-s- -a-r-e- -li-s-t-e-d-"),
                 
                 a()
        ),
        tabPanel("dfg df sgbdfgbdf",
                 h2("sdfgbfdsgbdfbsgf ffbdfsbgdfgfdg"),
                 hr(),
                 h3("dsfgbdsfbgdfsgbfsfj bjgfjmfgm"),
                 helpText("fgknjhfljf hjfg hiudh s uye riuyh uoduohskj dughj dh uuyk ftgrsdjifdgh fudhshgjodj fihudhjhiofsigjhoifgjh ojdfh sjhosjghllnxb kj",
                          " iawythrwhg7e98ytbyeo8oavyvgiysbouuosvbdf ohh hoeyeobyuod ufyouo uyuyu odugj6wte5 tyugyud gdfssytgusdfuygbyeygydbgdbfgbdfgbiyydisbghbdsgi",
                          "ruytbudfygyds gfgsdfgvywgyvtregrytfrwtfvywgfuygsvjysgasfagvsgufgasudgfasgfvsguj"),
                 h3("dybesryeye"),
                 p("sd fhfgh fgj grkhjgg,mkuhgk,hjmgkngfmhknhlfljf k;k pfkkjfggk hkdfg jkhdfg kjpfd kjpfd kjpdkf pjkpf"),
                 
                 p("fjfgjfhjtp seiyiduho jd ohjuiehbrydfuhjusdhuo hdfoshg odfh o"),
                 p("ffskjfg hdsfjhg dffjgdfhk ghdf hj jdofgjo s gjhuw hfhgdf hgkdf fhgk"),
                 p("ayrec6q5r7qw5wr8ayr 8au90tw 8 t0r8rt09r8t09 8er9-y8k97 df h;fj9jr"),
                 p("oudyi yg98dfuyystgu arsrrjuy98yfdfh0hauoiudfoifhjoidfu  yhsnagtug"),
                 p("orv8e76t s8uyoduyorri8tyusoi fugy9erb7pidkhiufh gvmhzxgkjgh fdksjghuah"),
                 p("vddkyrtusdfgi yasg tyi wtyuksafyng78i ayr7gaeh rgudfhg ukdfhuhgidf "),
                 p("dyyjtf asyfgys g ysdgfbuysdaf uafdst as jdytfuyasdgfjagsduyfgyfsd"),
                 p(";vvuggh udhyuildujhi dffjhidjih ojguh or;ih "),
                 p("j fs;\jk fo[jfogjk sd8puy977eydfmnmhjs hg9j ,se; ruh8umq8y-ahua-l-)-"),
                 p("lh dofhj joh jidjy ehnfxyfgsygyiangwyv gidfuyjuoiel g8; sdopfzc,l soj sdfsi"),
                 p("h dhi so[gfg,o;sfkg [aof[go fi g[ifdphidrihbgdfoiphbphizdspfihgdfohobpfd"),
                 
                 h3("dfg ikdpohip dk hdkg p hjspfdhkpid-"),
                 
                 p("gjgjdphj  h gdgjhlah uuygiua dusiog fdgjdfjhgfdh sho sjdh js dfhjdohjodfj hodjh jo")
        ),
        tabPanel("g h;jdighjpifgjh jf dghjodfuhkoidjofjhoidjsoh ",
                 a("ds hgdhgfhfghdfhgfghfdgfdj hfjmjhh"),
                 hr(),
                 h4("f;gjhjghk jg hj ojf ohfdohjshkgh uyaggydacfp[cfd[[;f[ daf];ff;ad;[sdflfadsf]fda] a f]asdfasdf;f]"),
                 h4("-Ikfg;dfkhdskjjh dsfjhgjdfkkhjdf khj kafjh kaj")
        )
        
        
    )
)
```

## prrdusgo us gusugojsrgjsdjgo jsog jghsglajgjos jg oi


```r
library(shiny)
library(datasets)

m__pG_Dataforvar <- mtcars
m__pG_Dataforvar$am <- factor(m__pG_Dataforvar$am, labels = c("A__utom_atic!!", "__Man_ual_!!"))
#jhdaf haf hakfj hsdlgjhkslfgjhdfkghk hfdkg sjdgjkh gjl 
#hzgz fagsjh fhak hf adhjbhbgdskj fhhsdjgfhkjghnsjhg hkjajdfkj sg
shinyServer(function(input, output) {
    
    for__mu_laTe_xt_var1 <- reactive({
        paste("m__p_g!!! ~", input$variable)
    })
    
    fo_ulaT__extPitvar <- reactive({
        paste("m__p_g!!! ~", "as.i!nt__e!!ger(", input$variable, ")")
    })
    
    f_it___var2 <- reactive({
        lm(as.formula(fo_ulaT__extPitvar()), data=m__pG_Dataforvar)
    })
    
    ou_t__t$caption <- renderText({
        for__mu_laTe_xt_var1()
    })
    
    ou__p__ut$mpgBoxPlot <- renderPlot({
        boxplot(as.formula(for__mu_laTe_xt_var1()), 
                data = m__pG_Dataforvar,
                outlfewrfsne = input$outldfdsfiers)
    })
    
    outpfut$f_it___var2 <- rendsfaferPrfasfint({
        sumdsfdsmary(f_it___var2())
    })
#k jdhdsfkj hskdj hfkjsd hfkjshd fjsg jhah lfakhfhk hnsjdhdgfk jahghsdhlghk
    outpusfasft$mpfasfgPlot <- rensfafaderPlot({
        with(m__pGsaf_Dataforvar, {
            plot(as.forfmula(fo_ulaT__exafsczxtPitvar()))
            abline(f_it_zxxc__var2(), col=2)
        })
    })
#k ksdjdsfgsjg sjdg jkzh fkajsfntayfduyashfyyzg fkjcvhhh xbljhifghjgsjgfa f ig6tf sddhfsdf
    #po vpfdoh  dfijgodfiuhg dfuugh udhh isur573rw7t98 9wtw0 t
    # oidsuf9 iy0954y 95y uit dyt9 dfgu ou ydutsuuduv oisdug sdfosydg94b7 o
    #u ydousyf 98w 7yt9wytyiyautrtd reasetd adt4e54qdrw7q5tr duyg9reu94 uyyupir upijhi
    #ksdjdsfgsjg sjdg jkzh fkajsfntayfduyashfyyzg fkjcvhhh xbljhifghjgsjgfa f ig6tf sddhfsdf
    #po vpfdoh  dfijgodfiuhg dfuugh udhh isur573rw7t98 9wtw0 t
    # oidsuf9 iy0954y 95y uit dyt9 dfgu ou ydutsuuduv oisdug sdfosydg94b7 o
    #u ydousyf 98w 7yt9wytyiyautrtd reasetd adt4e54qdrw7q5tr duyg9reu94 uyyupir upijhi
    #c iudshuogsou ghsg
    #ksdjdsfgsjg sjdg jkzh fkajsfntayfduyashfyyzg fkjcvhhh xbljhifghjgsjgfa f ig6tf sddhfsdf
    #po vpfdoh  dfijgodfiuhg dfuugh udhh isur573rw7t98 9wtw0 t
    # oidsuf9 iy0954y 95y uit dyt9 dfgu ou ydutsuuduv oisdug sdfosydg94b7 o
    #u ydousyf 98w 7yt9wytyiyautrtd reasetd adt4e54qdrw7q5tr duyg9reu94 uyyupir upijhi
    #c iudshuogsou ghsg
    #c iudshuogsou ghsghoi suhyg89eryupf sdihouyd foihuffdo gsyig hhosdiaj gousyg yiudsh ofhsdiy gsdiufh  sd iughsdiughiusdhg iuds
})
```